\documentclass[journal=jcisd8,manuscript=article]{achemso}


%=============== Packages ===================%

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{url}
\usepackage{tikz}
\usepackage[ruled]{algorithm2e}
\usepackage{flushend}
\usepackage{footnote}
\usepackage{threeparttable}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{amsthm}
\usepackage{setspace}
\usepackage{mhchem}
\usepackage{textcomp}


%TODO: GET THIS ON WEDNESDAY MORNING!!!
\newcommand{\caconc}{$10^{-4}$}

\title{CARBONIC ANHYDRASE: KINETICS OF Zn(II) REMOVAL BY 2,6-PYRIDINECARBOXYLATE}
\author{Paul Nickerson}
\email{pvnick@ufl.edu}
\affiliation[University of Florida]
{Department of Chemistry, University of Florida, Gainesville, Fl, US}

\doublespacing

\begin{document}

%=============== Abstract ==================%
\begin{abstract}
\singlespacing{
Carbonic Anhydrase is an enzyme which catalyzes the interconversion of carbon dioxide and carbonic acid/bicarbonate. It uses a zinc cofactor noncovalently bound to the active site for its catalytic activity. In this experiment, 2,6-pyridinecarboxylate (commonly referred to as dipic) was used to strip this ion from the enzyme, and kinetics of the involved mechanisms are investigated. An equilibrium constant is established, $K_{EML}$, which describes the binding affinity of the dipic ligand for the enzyme (forming a ternary complex) at $25^\circ{C}$ and 7.4pH. $K_{EML}$ was found to have a value of $(20\pm{18}){\ }M^{-1}$. In addition, a rate constant, $k_d$, is presented which describes the velocity of conversion from the ternary complex to the inactive form of the enzyme and the covalent zinc-dipic molecule. $k_d$ was found to have a value of $(0.10\pm{0.10}){\ }mins^{-1}$. These values are compared with those found in literature, and their chemical significance is discussed. Potential sources of error for these values are explored, along with possibilities for further investigation.
}
\end{abstract}

%=============== Content ===================%
\include{Introduction}
\include{Procedure}
\include{SampleCalculations}
\include{ErrorAnalysis}
\include{Results}
\include{Conclusion}

%=============== Reference ===================%
\newpage
\begin{thebibliography}{9}

\bibitem{bib:ca_ph_dependence}
  Lindskog, S; Coleman, J. E.
  \emph{Proc. Nat. Acad. Sci. USA.}
  \textbf{1973},
  \emph{70},
  2505 - 2508.
  
\bibitem{bib:pdb_carbonicanhydrase}
  RCSB Protein Data Bank.
  Refined structure of human carbonic anhydrase II at 2.0 A resolution.
  http://www.rcsb.org/pdb/explore/explore.do?structureId=1CA2 (accessed Jun 16, 2014).

\bibitem{bib:lab_manual}
  Killian, B. J.
  \emph{Experiments for Physical Chemistry Laboratory},
  Summer 2014,
  Target Copy: Gainesville,
  \textbf{2014}.
  45 - 50.

\bibitem{bib:lehninger_mm}
  Nelson, D. L.; Cox, M. M.
  \emph{Lehninger Principles of Biochemistry},
  5th ed.;
  W. H. Freeman: New York,
  2008.
  195 - 200.

\bibitem{bib:quantitative_chem_anal_beer_law}
  Harris, D. C.
  \emph{Quantitative Chemical Analysis},
  7th Ed.;
  W. H. Freeman: New York,
  2006.
  381.
  
\bibitem{bib:easy_peasy_values}
  Williams K. R; Adhyaru B.
  \emph{Journal of Chemical Education}
  \textbf{2004},
  \emph{81},
  1045 - 1047.

\end{thebibliography}

\end{document} 